ShrinkNets: Learning Network Size while Training

### 2018-02-09 paper/ICML/approach.tex
pass on s3

\section{The ShrinkNets Approach}

@@

At a high-level, our approach consists of two interconnected stages.
The first stage identifies neurons that do not improve the
prediction accuracy of the network and deactivates them. 
The second stage then {\it removes} neurons from the network (explicitly
shrinking weight matrices and updating optimizer state) thus leading to 
smaller networks and also faster inference times.

@@

\noindent\textbf{Neuron Removal: } During this stage, the neurons that are
deactivated by the switch layers are actually removed from the network,
effectively shrinking the network size. This step improves inference times, as
we demonstrate in our evaluation. We choose to remove neurons at training time
because we have observed that this allows the remaining active neurons to adapt
to the new network architecture and we can avoid a post-training step to prune
deactivated neurons.
% Existing techniques focus on neuron removal
% after training, and require an extra fine-tuning process to compensate for the
% removal.
% \srm{cite something?} \gl{I think we are fine or we could actually
% cite any of these paper}

In the remainder of this section we describe in detail the switch layer as well
as and the training process for \shrink, and 
then describe the removal process in Section~\ref{neuron_killing}.

>>>>

\section{The ShrinkNets Approach}
\label{sec:approach}

@@

At a high-level, our approach consists of two interconnected stages.
The first one identifies neurons that do not improve the
prediction accuracy of the network and deactivates them. 
The second stage then {\it removes} neurons from the network (explicitly
shrinking weight matrices and updating optimizer state) thus leading to 
smaller networks and faster inference.

@@

\noindent\textbf{Neuron Removal: } During this stage, the neurons that are
deactivated by the switch layers are actually removed from the network,
effectively shrinking the network size. This step improves inference times.
We choose to remove neurons at training time
because we have observed that this allows the remaining active neurons to adapt
to the new network architecture and we can avoid a post-training step to prune
deactivated neurons.

% Existing techniques focus on neuron removal
% after training, and require an extra fine-tuning process to compensate for the
% removal.
% \srm{cite something?} \gl{I think we are fine or we could actually
% cite any of these paper}

Next we describe in detail the switch layer as well as and the training process
for \shrink, and then describe the removal process in
Section~\ref{neuron_killing}.
